Machine Learning for Handwriting Recognition: Algorithms and Techniques

### 2023-11-15 Manuscript/Manuscript.tex
General Commits - Implemented Abstract

\section* {Abstract}
Will be Implemented after the article is finished.

\section* {Keywords}
Machine Learning, Deep Learning, Handwriting Recognition, Activation Function, Model, Parameters...

>>>>

\section* {Abstract}
This paper examines the interface between machine learning and handwriting recognition, an area that has grown significantly due to the development of powerful algorithms and sophisticated techniques. Despite the growing popularity of digital communications, handwriting remains a unique expression of personality that poses significant recognition challenges due to its variability and idiosyncrasies. This article explores the role of machine learning of basic concepts, data collection methods, data augmentation techniques, and various algorithmic approaches to handwriting recognition, including traditional machine learning and neural networks. The manuscript also discusses the impact of machine learning on the connection between human interactions and digital systems, highlighting its potential to improve user experience and facilitate digital interactions. By examining methods and advances in the field, this article reveals the future possibilities and applications of machine learning for accurately and efficiently processing handwritten text.

%\section* {Keywords}
%Machine Learning, Deep Learning, Handwriting Recognition, Activation Function, Model, Parameters...
